WI FastPlants: Heritability of number of cotelydons

### 2020-07-26 cotyledon-data-analysis.Rmd
changes to Rmd

>>>>

# New data: `Polycot-data-2020.csv` focusing on chi-square test

Creating categorical variable: dycots/polycots

```{r}
dat2 = data.frame(generation=dat$Generation)
dat2$cots = "dycot"
dat2$cots[dat$Cotyledons > 2] = "polycot"
dat2 = within(dat2, cots<-factor(cots))
summary(dat2)
write.table(dat2,file="data/polycot-data-2020-categories.csv", row.names = FALSE, sep=",")

dt = table(dat2$cots, dat2$generation)
```

### Data visualization
```{r}
library(graphics)
mosaicplot(dt, shade = TRUE, las=2, main="Cotelydons")
```

### Data analysis
```{r}
dt
ct = chisq.test(dt)

obs = ct$observed
exp = ct$expected

df = rbind(obs[1,],exp[1,],obs[2,],exp[2,],colSums(obs))
rownames(df) = c("dycot observed", "dycot expected", "polycot observed", "polycot expected", "total")

r = rowSums(obs)
ss = sum(r)
totals = c(r[1],NA,r[2],NA,ss)
cbind(df,totals)
ct$statistic
ct$p.value

## expected values
2437*2556/5585
2437*3029/5585
3148*2556/5585
3148*3029/5585
```
